Exploring Bounds

### 2015-04-09 draft.tex
added basic asymptotic bounds stuff

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
%\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{epstopdf}
%\usepackage{float}

@@

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

%\usepackage{graphicx}
%\usepackage{caption}
%\usepackage{epstopdf}
%\usepackage{float}

\newtheorem{theorem}{Theorem}
\numberwithin{theorem}{subsection}

@@

\section{Asymptotic Bounds}
We now wish to consider these $A_q(n,d)$ values as n goes to infinity.  To do so, we must more formally define two terms.

In class, we have considered the \textit{rate} of a linear code, $k/n$, as one measure of the goodness of a code.  That is,
the rate tells us how much information relative to redundancy that our codewords provide.  The concept of rate can be generalized
to non-linear codes as well.  For a possibly nonlinear code over $\mathbb{F}_q$ with $M$ codewords, the \textit{rate} is defined to be $n^{-1} \log_q {M}$.  Notice that
for an $[n,k,d]$ linear code, $M = q^k$ and hence the rate is $k/n$ as we expect.

A second notion of goodness that we have discussed, but I think not formally defined, is the \textit{relative distance} of a code.  For a linear or nonlinear code of length n
has minimum distance d, this value is the ratio $d/n$.

Consequently, for our asymptotic bounds, we are interested in the largest possible rate for a family of codes over $\mathbb{F}_q$ of lengths going to infinity with relative 
distances approaching some constant $\delta$.  In other words, we consider the equation:

\begin{equation}
\alpha_{q}(\delta) = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n)
\end{equation}

[What does this imply?]

\subsection{Asymptotic Singleton Bound}

Recall the Singleton Bound from lecture:

\begin{theorem}
For $d \le n$, $A_q(n,d) \le q^{n-d+1}$.
\end{theorem}

[explain what this means, what are the implications]

\begin{theorem}
If $0 \le \delta \le 1$, then $\alpha_q(\delta) \le 1 - \delta$.
\end{theorem} 
This theorem follows directly from the Singleton bound.

\begin{proof}
\begin{equation} 
\begin{split}
\alpha_{q}(\delta) & = \limsup_{n \to \infty} n^{-1} \log_q A_q(n,\delta n) \\
& \le \limsup_{n \to \infty} n^{-1} \log_q q^{n-\delta n+1} \\
& \le \limsup_{n \to \infty} \frac{n-\delta n+1}{n} \\
& \le 1 - \delta
\end{split}
\end{equation}
\end{proof}

\subsection{Asymptotic Plotkin Bound}
